TODO: Funky active learning pun

### 2025-01-09 doc/paper.tex
Finish first draft of introduction and background

This report focuses on comparing strategies in the image domain. It compares query strategies for a simple logistic regression model and a more complex CNN to study the effect of model complexity on the optimal query strategy. \textcolor{red}{CITATION were able to show that [QUERY METHODS] work well on simple models but do not generalize well on more complex models. To guarantee real-world applicability, knowledge about this needs to be gained as model complexities vary across different tasks and datasets}. Furthermore, the impact of different sizes of the initial annotated dataset is additionally investigated which is something that few studies analyze in combination. The effect of the combination between model complexity and initial annotated dataset size is a research gap in previously mentioned papers. \\

@@

% FROM HERE THIS IS NOT GOING TO BE PART OF THE FINAL PART
Previous papers do not: Is everything here now mentioned previously? if yes, then it can be deleted.

@@

	\item \cite{schröder_revisitinguncertaintybasedquerystrategies}: Does not compare across different sizes of the pool, and for simple models.
	\item \cite{comparativesurveydeepactive}: Does not compare impact of different initial train set size and strategies on shallow classifiers.

	\item \cite{werner_comparableactivelearning}: They focus on a wide range of domains, this paper only compares methods in the image domain. I compare strategies for a simple logistic regression model and a complex CNN across different starting sizes of the annotated dataset. \\
\end{itemize}
% TO HERE
The contributions of this paper are as follows:
\begin{itemize}
	\item \textbf{Systematic evaluation of active learning query strategies} on MNIST with a logistic regression model and CIFAR-10 using a CNN to analyze their behavior across datasets and model complexities.
	\item \textbf{Investigation of model complexity's influence} on the effectiveness of query strategies to provide knowledge into how shallow and deep models respond differently to active learning methods.
	\item \textbf{Analysis of the initial labeled dataset size's impact} on the performance of query strategies to simulate real-world scenarios such as starting completely from scratch, having a small labeled dataset or fine-tuning a model.
\end{itemize}

@@

\section{Cool ideas}
\begin{itemize}
	\item Show the typical framework of active learning in a figure in the introduction
\end{itemize}

@@

>>>>

This report focuses on comparing strategies in the image domain. It compares query strategies for a simple logistic regression model and a more complex CNN to study the effect of model complexity on the optimal query strategy. \\
It is uncertain whether query strategies which work well on simple models generalize well to more complex models like Neural Networks~\cite{schröder_surveyactivelearningtext}. To guarantee real-world applicability, knowledge about this needs to be gained as model complexities vary across different tasks and datasets. Furthermore, the impact of different sizes of the initial annotated dataset is additionally investigated which is something that few studies analyze in combination. The effect of the combination between model complexity and initial annotated dataset size is a gap not researched in previously mentioned papers. \\

@@

\\
\\
The contributions of this paper are as follows:

@@

	\item \textbf{Systematic evaluation of active learning query strategies} on MNIST with a logistic regression model and CIFAR-10 using a CNN to analyze their behavior across datasets and model complexities.
	\item \textbf{Investigation of model complexity's influence} on the effectiveness of query strategies to provide knowledge into how shallow and deep models respond differently to active learning methods.
	\item \textbf{Analysis of the initial labeled dataset size's impact} on the performance of query strategies to simulate real-world scenarios such as starting completely from scratch, having a small labeled dataset or fine-tuning a model.
\end{itemize}

@@

\newpage

\section{Cool ideas}
\begin{itemize}
	\item Show the typical framework of active learning in a figure in the introduction
	\item Accuracy vs. fraction of data size in relation to the datset (percentage of used data points)
\end{itemize}

@@

\section{Comparison to the other papers}
% FROM HERE THIS IS NOT GOING TO BE PART OF THE FINAL PART
Previous papers do not: Is everything here now mentioned previously? if yes, then it can be deleted.
\begin{itemize}
	\item \cite{schröder_revisitinguncertaintybasedquerystrategies}: Does not compare across different sizes of the pool, and for simple models.
	\item \cite{comparativesurveydeepactive}: Does not compare impact of different initial train set size and strategies on shallow classifiers.

	\item \cite{werner_comparableactivelearning}: They focus on a wide range of domains, this paper only compares methods in the image domain. I compare strategies for a simple logistic regression model and a complex CNN across different starting sizes of the annotated dataset. \\
\end{itemize}
% TO HERE
